\section{Introduction}

The mouse shares its majority protein encoding genes with human and is arguably one of the most popular research models for human disease. Wide spread use of mouse models in biomedical research can not be understated. \cite{MORSEIII_2007} One significant benefits of utilizing a rodent model is fast and economical breading in captivity \cite{Rosenthal_2007}, which allows fast tract experimental results. \cite{Vandamme_2014} Without the doubts, mouse (also other rodents) has many physiological features and pathological pathways that are very similar to human including vital nervous, cardiovascular and immune system, which make mouse a good representative models of human pathology. \cite{MORSEIII_2007,Rosenthal_2007}

Dispite the dominant application of mouse models in biomedical researches, recent studies have also highlighted the high degree divergence between human and mouse genome in regarding to transcription regulations. \cite{25409824} This posts an important question about whether default mouse models are the best representation to study all human diseases. In this article, we are using bioinformatic pipeline to examine the substrate degradome difference between human and mouse in the context of dipeptidyl dipeptidase-4 (DPP4).  

DPP4 is exoprotease in nature and is able to cleave first two amino acid from substrate's N-terminus. However, DPP4 is a unique protease, which has rare ability to cleave penultimate proline. From our current knowledge, human and mouse's DPP4 has conserved catalytic specificity. Here poses a question, if many human DPP4 substrates do not have an exact representation in mouse, particularly if N-terminus is not conserved, a deemed DPP4 substrate in mouse model is not likely to be a human substrate. Despite the many years research in DPP4 research, there is limited \textit{in vivo} evidence has been depicted using mouse model. Maybe, just maybe, mouse is not a perfect model for studying DPP4's pathological role in human. 

\cite{Justice_2011}